Portfolios of Subgraph Isomorphism Algorithms

### 2015-12-12 paper/paper.tex
reformatting of table and small fixes

\usepackage{times}
\usepackage{complexity}
\usepackage{hyperref}
\usepackage{microtype}
\usepackage{cleveref}                  % no need to type Figure etc
\usepackage{xcolor,colortbl}

@@

\section{Definitions and notations}

@@

\section{Subgraph isomorphism algorithms}

@@

\subsection{Filtering for subgraph isomorphism}

@@

\subsection{Propagation of invariant properties}

@@

\subsection{Experimental setup}

@@

\subsection{Algorithms selected in our portfolio}

@@

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{figures/ecdf-glasgow}
\caption{Empirical cumulative distribution function for the Glasgow algorithm
with path lengths 1, 2, 3, and 4.}
\label{fig:ecdf-glasgow}
\end{figure}

Figure~\ref{fig:ecdf-glasgow} shows the cumulative distribution function for the
Glasgow algorithm with four different path lengths. As the instances become
harder to solve, longer paths become better. This is what we expect, as more
reasoning is expensive, but potentially increases the reduction of the search
space. In particular, the relative performance of the algorithms is monotone in
the time it takes to solve the instance---path length 1 is best at first, but
gets worse as the time to solve the instance increases until path length 2 is
better. After that point, length 1 is never better than length 2 again. The same
is true for the other path lengths.

The figure illustrates the potential for portfolios and algorithm selection we
have. There is clearly no path length that dominates throughout. Therefore, we
consider 4 different instances of the Glasgow algorithm here, with path lengths
varying from 1 to 4.

@@

\subsection{Results from Individual Algorithms} \label{expComp}

@@

Table \ref{expClass} shows us that we cannot reasonably split things up based upon which class instances are coming from, unlike SAT. For all classes, there are always at least 2 algorithms which are the best for at least one instance of the class. In particular, for classes 2 and 3, each algorithm is the best for at least one instance (except Glasgow 4 for Class 3).

\begin{table}[t]
\begin{center}
\begin{tabular}{|c||r||r|r|r||r|r|r|r|}
\hline
Class & VF2 & \multicolumn{3}{c||}{LAD} & \multicolumn{4}{c|}{Glasgow}\\
&&incomplete&default&path&1&2&3&4\\\hline\hline
1 &        0 &       20 &        0 &        0 &       80 &        0 &        0 &        0 \\\hline
2 &      201 &       92 &      189 &      270 &      520 &      180 &       53 &       15 \\\hline
3 &      112 &     1608 &      617 &      959 &      396 &      195 &       21 &        0 \\\hline
4 &      270 &        0 &        0 &        0 &        5 &        0 &        0 &        0 \\\hline
5 &      266 &        0 &        1 &        3 &       31 &        0 &        0 &        0 \\\hline
6 &       71 &        0 &        0 &        0 &        7 &       14 &        1 &        0 \\\hline
7 &      270 &        0 &        0 &        0 &        5 &        0 &        0 &        0 \\\hline
8 &        0 &        0 &        0 &        1 &      195 &       69 &        6 &        0 \\\hline
9 &       77 &        3 &        0 &       19 &      103 &        1 &        0 &        0 \\\hline
10 &       13 &        0 &        2 &        2 &        7 &        0 &        0 &        0 \\\hline
11 &        2 &      142 &       71 &       17 &       23 &        0 &        0 &        0 \\\hline
12 &        0 &        0 &        1 &        2 &      158 &        6 &        1 &        0 \\\hline\hline
Total & 1282 & 1865 & 881 & 1273 & 1530 & 465 & 82& 15\\\hline
\end{tabular}
\end{center}
\caption{Number of times each algorithm is best, for each class.\label{expClass}}
\end{table}

@@

\subsection{Solver Selection}

@@

\subsection{Portfolios for different timeouts}

>>>>

\usepackage{times}
\usepackage{complexity}
\usepackage{hyperref}
\usepackage{microtype}
\usepackage{cleveref}                  % no need to type Figure etc
\usepackage{xcolor,colortbl}
\usepackage{tabularx}

@@

\section{Definitions and Notations}

@@

\section{Subgraph Isomorphism Algorithms}

@@

\subsection{Filtering for Subgraph Isomorphism}

@@

\subsection{Propagation of Invariant Properties}

@@

\subsection{Experimental Setup}

@@

\subsection{Portfolio Composition}

@@

@@

\subsection{Results for Individual Algorithms} \label{expComp}

@@

Table \ref{expClass} shows us that we cannot reasonably split things up based upon which class instances are coming from, unlike SAT. For all classes, there are always at least 2 algorithms which are the best for at least one instance of the class. In particular, for classes 2 and 3, each algorithm is the best for at least one instance (except Glasgow 4 for class 3).

\begin{table}[t]
\begin{center}
\begin{tabularx}{.8\textwidth}{XXrXrrrXrrrr}
\toprule
Class && VF2 && \multicolumn{3}{c}{LAD} && \multicolumn{4}{c}{\hspace*{2em}Glasgow}\\
&&&&incomplete&default&path&&1&2&3&4\\
\midrule
1 &&        0 &&       20 &        0 &        0 &&       80 &        0 &        0 &        0 \\
2 &&      201 &&       92 &      189 &      270 &&      520 &      180 &       53 &       15 \\
3 &&      112 &&     1608 &      617 &      959 &&      396 &      195 &       21 &        0 \\
4 &&      270 &&        0 &        0 &        0 &&        5 &        0 &        0 &        0 \\
5 &&      266 &&        0 &        1 &        3 &&       31 &        0 &        0 &        0 \\
6 &&       71 &&        0 &        0 &        0 &&        7 &       14 &        1 &        0 \\
7 &&      270 &&        0 &        0 &        0 &&        5 &        0 &        0 &        0 \\
8 &&        0 &&        0 &        0 &        1 &&      195 &       69 &        6 &        0 \\
9 &&       77 &&        3 &        0 &       19 &&      103 &        1 &        0 &        0 \\
10 &&       13 &&        0 &        2 &        2 &&        7 &        0 &        0 &        0 \\
11 &&        2 &&      142 &       71 &       17 &&       23 &        0 &        0 &        0 \\
12 &&        0 &&        0 &        1 &        2 &&      158 &        6 &        1 &        0 \\
\midrule
Total && 1282 && 1865 & 881 & 1273 && 1530 & 465 & 82& 15\\
\bottomrule
\end{tabularx}
\end{center}
\caption{Number of times each algorithm is best, for each class.\label{expClass}}
\end{table}

@@

\subsection{Selection Model}

@@

\subsection{Portfolios for Different Timeouts}
